Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-04-30 paper.tex
working no kswapd section

TODO: in progress... should be ready for final product...

>>>>

Figure (TODO) shows the total number of jiffies spent running kswapd as the
number of operations performed increases. Figure (TODO) shows the same for
khugepaged. Notice that one jiffy corresponds to 10ms of runtime.

We find that although kswapd does not take up a significant
percentage of runtime compared with the applcation, it does still take
siginficant amounts of time and use system resources. This is especially true
during times of high memory pressure.

We also found that kswapd's behavior heavily depends on whether huge pages are
enabled or not.
